---
title: "Course Project 1"

date: "12 June 2016"
output: md_document
---


1. load the data from local disk and display basic information
```{r}

mydata <- read.csv("c:\\project\\activity_data\\activity.csv")
summary(mydata)

```

2.Histogram of the total number of steps taken each day. 

```{r}
totalStepsPerDay<-aggregate(mydata$steps, by=list(date=mydata$date), FUN=sum)
totalStepsPerDay<-aggregate(mydata$steps, by=list(date=mydata$date), FUN=sum,na.rm=TRUE)
hist(totalStepsPerDay$x, xlab="step per day",main="histogram for total activity per day")
```


3. mean and median number of steps taken each day
```{r}

 mean(totalStepsPerDay$x)

 median(totalStepsPerDay$x)
  
```
4.Time series plot of the average number of steps taken
  
```{r}
 
  time_series <- tapply(mydata$steps, mydata$interval, mean, na.rm = TRUE)
  
   plot(row.names(time_series), time_series, type = "l", xlab = "5-min interval", 
      ylab = "Average across all Days", main = "Average number of steps taken", 
      col = "red")
```

5. The 5-minute interval that, on average, contains the maximum number of steps
```{r}
 max_interval <-which.max(time_series)
names(max_interval)

```

get count of the na data
```{r}
activity_NA <- sum(is.na(mydata))
activity_NA
```

6. replace missing data with interval average
```{r}
StepsAverage <- aggregate(steps ~ interval, data = mydata, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(mydata)) {
    obs <- mydata[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(StepsAverage, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fillNA <- c(fillNA, steps)
}
```

prepare na data
```{r}
 new_activity <- mydata
 new_activity$steps <- fillNA
```

7. Histogram of the total number of steps taken each day after missing values are imputed
```{r}
 StepsTotal2 <- aggregate(steps ~ date, data = new_activity, sum, na.rm = TRUE)
 hist(StepsTotal2$steps, main = "Total steps by day", xlab = "day", col = "red")
```
 
 
 mean 
 
```{r}
 
 mean(StepsTotal2$steps)
```
 
 
 
 median
 
```{r}
 median(StepsTotal2$steps)
```
 
 8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
new_activity$type_of_day <- weekdays(as.Date(new_activity$date))
new_activity$type_of_day[new_activity$type_of_day  %in% c("Saturday","Sunday") ] <- "weekend"
new_activity$type_of_day[new_activity$type_of_day != "weekend"] <- "weekday"
 new_activity_interval <- aggregate(steps ~ interval + type_of_day, new_activity, mean)
```
 
plot 
```{r}
  library(lattice)
 xyplot(steps ~ interval |type_of_day, new_activity_interval, type = "l", layout = c(1, 2), 
        xlab = "Interval", ylab = "Number of steps")
 ```
 